### 2024-03-25 thesis/sections/5.2-re-generation.tex
results

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|ccc|ccc|ccc}
        \toprule
                  &           & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}} & \multicolumn{3}{c}{\textbf{CLEVR colour}}                                                                                         \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        $LSTM\_o$ & $LSTM\_e$ & \textbf{Acc.}                       & \textbf{F1}                         & \textbf{NT}                               & \textbf{Acc.} & \textbf{F1} & \textbf{NT} & \textbf{Acc.} & \textbf{F1} & \textbf{NT} \\\midrule
        {100}     & {30}      & {38}                                & {41,16}                             & {40}                                      & {14}          & {48,91}     & {34}        & {15}          & {36,98}     & {34}        \\
        {1500}    & {15}      & {45}                                & {62,66}                             & {45}                                      & {17}          & {51,89}     & {38}        & {13}          & {35,85}     & {33}        \\
        {2000}    & {10}      & {45}                                & {60,72}                             & {44}                                      & {16}          & {50,77}     & {37}        & {13}          & {34,96}     & {36}        \\
        \bottomrule
    \end{tabular}
    \caption{Overall accuracies (Acc.), F1-Score (F1) and non-target accuracies (NT) in \% of the basic RE generator after 30 epochs for selected configurations: $LSTM_o$ are different LSTM output sizes and $LSTM_e$ are different embedding sizes for the tokens in the LSTM.}
    \label{tab:results:basic-re-generator}
\end{table}

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|ccc|ccc|ccc}
        \toprule
                  &           & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}} & \multicolumn{3}{c}{\textbf{CLEVR color}}                                                                                         \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        $LSTM\_o$ & $LSTM\_e$ & \textbf{Acc.}                       & \textbf{F1}                         & \textbf{NT}                              & \textbf{Acc.} & \textbf{F1} & \textbf{NT} & \textbf{Acc.} & \textbf{F1} & \textbf{NT} \\\midrule
        {100}     & {30}      & {38}                                & {41,16}                             & {40}                                     & {14}          & {48,91}     & {34}        & {15}          & {36,98}     & {34}        \\
        {1500}    & {15}      & {45}                                & {62,66}                             & {45}                                     & {17}          & {51,89}     & {38}        & {13}          & {35,85}     & {33}        \\
        {2000}    & {10}      & {45}                                & {60,72}                             & {44}                                     & {16}          & {50,77}     & {37}        & {13}          & {34,96}     & {36}        \\
        \bottomrule
    \end{tabular}
    \caption{Overall accuracies (Acc.), F1-Score (F1) and non-target accuracies (NT) in \% of the basic RE generator after 30 epochs for selected configurations: $LSTM_o$ are different LSTM output sizes and $LSTM_e$ are different embedding sizes for the tokens in the LSTM.}
    \label{tab:results:basic-re-generator}
\end{table}
